Normal States Training for High Accuracy Event Detection

### 2016-06-13 paper/main.tex
solve the problem of how to start the model

\begin{equation}
\label{eq:LDAgibbs}
\begin{aligned}
&p(z_{dn}=k|w_{dn}=v,z_{\neg{dn}},w_{\neg{dn}},\alpha,\beta,\tau)\\
&\ \ \propto \frac{n_{dk}+\alpha}{n_{d,.}+K\alpha}\frac{n_{kv}+\tau_{kv}+\beta}{n_{k,.}+\tau_{k,.}+V\beta}
\end{aligned}
\end{equation}
\begin{comment}
\begin{algorithm}[H]
    \caption{UPIETM batch learning algorithm} %title
    \label{alg:UPIETMbatch} %label
    \begin{algorithmic}[1] %this 1 means the showing of line number in algorithm
    \STATE initiate the topic label and the statistics
    \FOR {\(i=1:I_1\)}
        \FOR{\(u\) in  user set U}
            \FOR{\(n\) = \(1:P_u\)}
                \STATE sample profile's hidden topic \(s_{un}\) by (\ref{timeUserTagLDAIVsamplingForS})
                \STATE update \(s_{un}\), \(c^{(p)}_{u,k}\) and \(c^{(p)}_{k,v}\)
            \ENDFOR%end of n
        \ENDFOR%end of u
    \ENDFOR%end of i
    \FOR{iteration \(i=1:I_2\)}
        \FOR{\(t=1:T\)}
            \FOR{\(u\) in  user set \(U_t\)}
                \FOR{\(d\) = \(1: D_u\) }
                    \STATE{sample \(y_{ud}\) and \(z_{ud}\) by (\ref{timeUserTagLDAIVJointSamplingForY0Z}), (\ref{timeUserTagLDAIVJointSamplingForY1Z}) }
                    \IF{\(y_{ud}=0\)}
                        \STATE{update \(z_{ud}\), \(y_{ud}\), \(c^{(0)}_u\), \(c^{(0)}_{u,k}\), \(c^{(0)}_{k,v}\)}
                    \ELSE
                        \STATE{update \(z_{ud}\), \(y_{ud}\), \(c^{(1)}_u\), \(c^{(1)}_{t,k}\), \(c^{(1)}_{t,k,v}\)}
                    \ENDIF
                    \FOR{\(n\) in \(1,\cdots,N_{ud}\)}
                        \STATE{sample \(x_{udn}\) by (\ref{timeUserTagLDAIVsamplingX0}), (\ref{timeUserTagLDAIVsamplingX1}})
                        \IF{\(x_{udn}=0\)}
                            \STATE{update \(x_{udn}\), \(M^{\rho}_0\), \(c^{(B)}_v\)}
                        \ELSE
                            \STATE{update \(x_{udn}\), \(M^{\rho}_1\), \(c^{(0)}_{k,v}\), \(c^{(1)}_{t,k,v}\) }
                        \ENDIF
                    \ENDFOR%end of n
                \ENDFOR%end of d
            \ENDFOR%end of u
        \ENDFOR%end of t
    \ENDFOR%end of i
    \end{algorithmic}
\end{algorithm}
\end{comment}

>>>>

\begin{equation}
\label{eq:LDAgibbs}
\begin{aligned}
&p(z_{dn}=k|w_{dn}=v,z_{\neg{dn}},w_{\neg{dn}},\alpha,\beta,\tau)\\
&\ \ \propto (n_{dk}+\alpha)\frac{n_{kv}+\tau_{kv}+\beta}{n_{k,.}+\tau_{k,.}+V\beta}
\end{aligned}
\end{equation}
\begin{comment}
\begin{algorithm}[H]
    \caption{UPIETM batch learning algorithm} %title
    \label{alg:UPIETMbatch} %label
    \begin{algorithmic}[1] %this 1 means the showing of line number in algorithm
    \STATE initiate the topic label and the statistics
    \FOR {\(i=1:I_1\)}
        \FOR{\(u\) in  user set U}
            \FOR{\(n\) = \(1:P_u\)}
                \STATE sample profile's hidden topic \(s_{un}\) by (\ref{timeUserTagLDAIVsamplingForS})
                \STATE update \(s_{un}\), \(c^{(p)}_{u,k}\) and \(c^{(p)}_{k,v}\)
            \ENDFOR%end of n
        \ENDFOR%end of u
    \ENDFOR%end of i
    \FOR{iteration \(i=1:I_2\)}
        \FOR{\(t=1:T\)}
            \FOR{\(u\) in  user set \(U_t\)}
                \FOR{\(d\) = \(1: D_u\) }
                    \STATE{sample \(y_{ud}\) and \(z_{ud}\) by (\ref{timeUserTagLDAIVJointSamplingForY0Z}), (\ref{timeUserTagLDAIVJointSamplingForY1Z}) }
                    \IF{\(y_{ud}=0\)}
                        \STATE{update \(z_{ud}\), \(y_{ud}\), \(c^{(0)}_u\), \(c^{(0)}_{u,k}\), \(c^{(0)}_{k,v}\)}
                    \ELSE
                        \STATE{update \(z_{ud}\), \(y_{ud}\), \(c^{(1)}_u\), \(c^{(1)}_{t,k}\), \(c^{(1)}_{t,k,v}\)}
                    \ENDIF
                    \FOR{\(n\) in \(1,\cdots,N_{ud}\)}
                        \STATE{sample \(x_{udn}\) by (\ref{timeUserTagLDAIVsamplingX0}), (\ref{timeUserTagLDAIVsamplingX1}})
                        \IF{\(x_{udn}=0\)}
                            \STATE{update \(x_{udn}\), \(M^{\rho}_0\), \(c^{(B)}_v\)}
                        \ELSE
                            \STATE{update \(x_{udn}\), \(M^{\rho}_1\), \(c^{(0)}_{k,v}\), \(c^{(1)}_{t,k,v}\) }
                        \ENDIF
                    \ENDFOR%end of n
                \ENDFOR%end of d
            \ENDFOR%end of u
        \ENDFOR%end of t
    \ENDFOR%end of i
    \end{algorithmic}
\end{algorithm}
\end{comment}
